### 2015-08-02 simulation.Rmd
updated Ne to proper value in shape/

Here is the Hessian of the likelihood (obtained by numerical differentiation)
```{r likelihood_hessian, echo=FALSE}
# Hessian of the likelihood surface
likfun.hess <- hessian(function(x)fit.model@likfun(x*timevec[fit.model@results$use.par]),method.args=list(eps=min(coef(model)/10)),x=coef(model)[fit.model@results$use.par])
colnames( likfun.hess ) <- rownames( likfun.hess ) <- names(coef(fit.model))[fit.model@results$use.par]
pander(likfun.hess)
```
and its inverse (the asymptotic covariance matrix)
```{r likelihood_covariance, echo=FALSE}
# asymptotic covariance matrix
est.covmat <- ginv(likfun.hess)
pander(est.covmat)
```
and the corresponding correlation matrix
```{r likelihood_correlation, echo=FALSE}
# asymptotic covariance matrix
pander(cov2cor(est.covmat))
```

>>>>

Here is the Hessian of the likelihood (obtained by numerical differentiation)
```{r likelihood_hessian, echo=FALSE}
# Hessian of the likelihood surface
likfun.hess <- hessian(function(x)model@likfun(x*timevec[model@results$use.par]),method.args=list(eps=min(coef(model)/10)),x=coef(model)[model@results$use.par])
colnames( likfun.hess ) <- rownames( likfun.hess ) <- names(coef(model))[model@results$use.par]
pander(likfun.hess)
```
and its inverse (the asymptotic covariance matrix)
```{r likelihood_covariance, echo=FALSE}
# asymptotic covariance matrix
est.covmat <- ginv(likfun.hess)
pander(est.covmat)
```
and the corresponding correlation matrix
```{r likelihood_correlation, echo=FALSE}
# asymptotic covariance matrix
pander(cov2cor(est.covmat))
```
